### 2012-02-16 2.tex
Spacing in appendices.

>>>>

%lexicon
The \emph{lexicon} has many senses: throughout, I use the term to refer to the set of underlying representations \citep[][269]{LANGUAGE}, but I depart from \citeauthor{LANGUAGE}'s understanding by further adopting the assumption that this set is merely a reflection of individual speakers' knowledge of their language, realized in the human mind; it has no further reality.
